---
title: "Linear Model"
author: "Deniss Gonzalez Ramirez"
date: "11/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression


### Scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The scatterplot above shows that there is a linear trend going uphill and to the right which is a sign of a positively correlated set of data. The greater the pounds of arm force(ARM), the greater the simulation score (SIMS).


#### Scatterplot with model fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
``` 


The plot above shows that this is the best fit line for our data. It shows that if we are looking for an x-value of 88 and a y-value of 0.7 it is predicted to fall into place.


### Numerical Results
```{r}
cor(SIMS~ARM,data=data)
```

The number above indicates the correlation between the measure SIMdata <- ggplot(data,aes(y=SIMS,x=ARM))
S score and ARM force. Correlation is a measure of the linear association between the two variables. 



### Inferential Results
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The equation is SIMS = -4.095160 + 0.054563 * ARM 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")

```



## SIMS~GRIP Regression




## SIMS~ARM+GRIP Regression



## Model Comparisons


