---
title: "Linear Model"
author: "Deniss Gonzalez Ramirez"
date: "11/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression


### Scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The generic scatter plot above shows that there is a linear trend going uphill and to the right which is a sign of a positively correlated set of data. The greater the pounds of arm force(ARM), the greater the simulation score (SIMS).


## GGPlot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 


The scatter plot above shows the SIMS result as a function of ARM. The data points are each individual score and corresponding arm strength. The blue line indicates the best linear fit to predict SIMS as a function of line. The shaded area is the uncertainty associated with where that blue line would be if you repeated the experiment a large number of times. 
  

### Numerical Results
```{r}
cor(SIMS~ARM,data=data)
```

The number above indicates the correlation between the measure SIMdata <- ggplot(data,aes(y=SIMS,x=ARM))
S score and ARM force. Correlation is a measure of the linear association between the two variables. 



### Inferential Results
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The equation is SIMS = -4.095160 + 0.054563 * ARM 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")

```

Fit is the predicted ARM score when you have an ARM strength of 88.

The lwr and upr are the 95% confidence intervals for the predicted SIMS scores when ARM score is 88.

## SIMS~GRIP Regression


### Scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

The generic scatter plot which depicts SIMS score and GRIP above shows that there is a concentration in the middle. 


## GGPlot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 


The scatter plot above shows the SIMS result as a function of GRIP. The data points are each individual score and corresponding arm strength. The blue line indicates the best linear fit to predict SIMS as a function of line. The shaded area is the uncertainty associated with where that blue line would be if you repeated the experiment a large number of times. 
  

### Numerical Results
```{r}
cor(SIMS~GRIP,data=data)
```

The number above indicates the correlation between the measure SIMdata <- ggplot(data,aes(y=SIMS,x=GRIP))
S score and GRIP force. Correlation is a measure of the linear association between the two variables. 



### Inferential Results
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```


The equation is SIMS = -4.809675 + 0.045463 * GRIP 


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,newData,interval="prediction")

```

Fit is the predicted SIMS score when you have a GRIP strength of 94.

The lwr and upr are the 95% confidence intervals for the predicted SIMS scores when GRIP strength is 94.

Comparing the two models, model 1 with model 2:

model 1(SIMS~ARM) has a slightly lower residual standard error score of 1.226 while model 2(SIMS~GRIP) has a score of 1.295.

model 1(SIMS~ARM) has a higher adjusted r squared score of 0.467 while model2(SIMS~GRIP) scored a lower 0.4053

In this case it appears to be that model 1 is slightly better because it has a smaller residual standard error and a higher adjusted R-squared value.



## SIMS~ARM+GRIP Regression


```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
``` 

This model appears to be a good fit because the adjusted R-squared value and the residual standard error was smaller than the previous models (1 and 2).



## Inferential Test

This is the inferential test to compare all models. The test is anova.

$H_0$: There is no difference in the models and their ability to predict the data. Both of them can predict the data (SIMS) equally.

$H_A$: There is a difference in how well the models(model1 and model2) are able to predict the data.


```{r}
anova(model.2,model.3)
```

The p value is 0.000000001495 which is a very small number. 

We reject the null hypothesis because we have evidence that model 3 is better than model 2. There is a difference between how well the models are able to interpret the data.


## Model Comparisons


